The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-11-12 talk/vmil2012/paper.tex
cleanup
update authors in pdfinfo

\ifpdf
\usepackage[pdfpagelabels=true,hidelinks]{hyperref}
\hypersetup{%
  plainpages=false,%
  pdftitle={The Efficient Handling of Guards in the Design of RPython's Tracing JIT},%
  pdfauthor={David Schneider},
}
\else
\usepackage[hyphens]{url}
\fi

@@

%Section~\ref{sec:Evaluation} presents Figures about the absolute number of
%operations for each benchmark, and the overhead produced by the information
%stored at the different levels for the guards
In this paper we want to substantiate the aforementioned observations about guards and
describe based on them the reasoning behind their implementation in
RPython's tracing just-in-time compiler. The contributions of this paper are:
\begin{itemize}
  \item An analysis of guards in the context of RPython's JIT,
  \item detailed measurements about the frequency and the
  memory overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of RPython's JIT and a description of the rationale behind the design.
\end{itemize}

@@

%\todo{Figure needs better formatting}
\begin{figure}[ht]
  \noindent
  \centering
  \begin{minipage}{1\columnwidth}
\begin{lstlisting}[xleftmargin=20pt,xrightmargin=20pt,framexleftmargin=5pt,framexrightmargin=-10pt,mathescape, numbers=right, escapechar=|, firstnumber=18,frame=b]
$b_3$ = int_eq($i_5$, 1)                    |\setcounter{lstnumber}{17}|
guard_false($b_3$)                          |\setcounter{lstnumber}{-1}|
\end{lstlisting}
  \end{minipage}
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
MOVEQ r8, #1
MOVNE r8, #0
...
CMP r8, #0
BEQ <bailout>
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
BNE <bailout>
...
...
...
...
    \end{lstlisting}
  \end{minipage}
  \caption{Result of separated (left) and merged (right) compilation of one guard and the following operation (top).}
  \label{fig:trace-compiled}
\end{figure}

@@

%\section*{Appendix}

%\todo{remove this section and the figures}
%\begin{figure*}
%    \include{figures/ops_count_table}
%    \caption{Relative numbers of operations in the traces generated for
%    different benchmarks}
%    \label{fig:ops_count}
%\end{figure*}
%\begin{figure*}
%\centering
%\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
%\caption{Relative frequency of operations before and after optimization}
%\label{fig:ops_pie}
%\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
%\listoftodos
\end{document}

>>>>

\ifpdf
\usepackage[pdfpagelabels=true,hidelinks]{hyperref}
\hypersetup{%
  plainpages=false,%
  pdftitle={The Efficient Handling of Guards in the Design of RPython's Tracing JIT},%
  pdfauthor={David Schneider and Carl Friedrich Bolz},
}
\else
\usepackage[hyphens]{url}
\fi

@@

In this paper we want to substantiate the aforementioned observations about guards and
describe based on them the reasoning behind their implementation in
RPython's tracing just-in-time compiler. The contributions of this paper are:
\begin{itemize}
  \item An analysis of guards in the context of RPython's JIT,
  \item detailed measurements about the frequency and the
  memory overhead associated with guards, and
  \item a description about how guards are implemented in the high\-
  and low-level components of RPython's JIT and a description of the rationale behind the design.
\end{itemize}

@@

\begin{figure}[ht]
  \noindent
  \centering
  \begin{minipage}{1\columnwidth}
\begin{lstlisting}[xleftmargin=20pt,xrightmargin=20pt,framexleftmargin=5pt,framexrightmargin=-10pt,mathescape, numbers=right, escapechar=|, firstnumber=18,frame=b]
$b_3$ = int_eq($i_5$, 1)                    |\setcounter{lstnumber}{17}|
guard_false($b_3$)                          |\setcounter{lstnumber}{-1}|
\end{lstlisting}
  \end{minipage}
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
MOVEQ r8, #1
MOVNE r8, #0
...
CMP r8, #0
BEQ <bailout>
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{.40\columnwidth}
    \begin{lstlisting}
CMP r6, #1
BNE <bailout>
...
...
...
...
    \end{lstlisting}
  \end{minipage}
  \caption{Result of separated (left) and merged (right) compilation of one guard and the following operation (top).}
  \label{fig:trace-compiled}
\end{figure}

@@

\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\end{document}
